This is a title

### 2021-05-13 manuscript/ms.tex
adds draft of theory section

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}

@@

\section{Theory}
\label{sec:theory}
Throughout this work, we will utilize a modified version of the Boussinesq equations of motion, similar to the model derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In dimensional form,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho'}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad = \chi\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
\label{eqn:temperature} \\
&\frac{\rho'}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
In this model, $\rho_0$ is a (constant) background density and $\rho'$ are fluctuations which act only in the buoyancy force and varies linearly with the temperature $T$ according to the coefficient of thermal expansion, $\alpha = \partial\ln\rho / \partial T$.
Furthermore, $\vec{u}$ is the velocity vector, $\nu$ and $\chi$ are respectively the viscous and thermal diffusivity, $Q$ is a bulk internal heating term [CITE], and $\gradad$ is the adiabatic temperature gradient (we define $\gradad$ as a positive value to align with stellar structure conventions; this means marginal stability is achieved when $\partial_z T = -\gradad$).
We modify the model of \citet{spiegel_veronis_1960} to allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
We assume that the classical thermal diffusion term $\chi \grad^2 T'$  only acts on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$.

\section{Simulation Details}
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}} = (\Pran\mR)^{-1}\grad^2 T' + \grad\dot[k \grad \overline{T}] + Q
\end{align}

>>>>

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}

@@

\section{Theory}
\label{sec:theory}
Throughout this work, we will utilize a modified version of the Boussinesq equations of motion, similar to the model derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In dimensional form,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho'}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho'}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
In this model, $\rho_0$ is a (constant) background density and $\rho'$ are fluctuations which act only in the buoyancy force and varies linearly with the temperature $T$ according to the coefficient of thermal expansion, $\alpha = \partial\ln\rho / \partial T$.
Furthermore, $\vec{u}$ is the velocity vector, $\nu$ and $\chi$ are respectively the viscous and thermal diffusivity, $Q$ is a bulk internal heating term [CITE], and $\gradad$ is the adiabatic temperature gradient (we define $\gradad$ as a positive value to align with stellar structure conventions; this means marginal stability is achieved when $\partial_z T = -\gradad$).
We modify the model of \citet{spiegel_veronis_1960} to allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
We assume that the classical thermal diffusion term $\chi \grad^2 T'$  only acts on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$.

The basis of the theory of \citet{zahn1991} is that the size of the convection zone is determined by the horizontally-averaged energetics and buoyancy breaking.
We assume convection reaches a time-stationary, equilibrium state; we vertically integrate Eqn.~\ref{eqn:temperature} and take a horizontal average to find
\begin{equation}
\Ftot = \Frad + \Fconv = \int Q dz + \Fbot,
\end{equation}
with $\Fconv = \overline{w T}$ and $\Fbot$ the flux at the bottom of the convective domain and $\Ftot$ the total flux, which can vary in height according to integral of $Q$.
We next assume that convection penetrates above the nominal schwarzschild boundary of the convection zone and mixes the temperature gradient towards the adiabatic in that region.
Thus, in that region, the convective flux can be found,
\begin{equation}
\Fconv = \Ftot - F_{\rm{rad, ad}} = \Ftot - k \grad_{\rm{ad}}.
\end{equation}
By definition, in this region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, where $\grad_{\rm{rad}} = \Ftot/k$, so this requires that $\Fconv < 0$ in the convective penetration region.
We next assume that the temperature and velocity are highly correlated in the penetrative region with very similar horizontal fluctuations,
\begin{equation}
w(x,y,z) = W(z)h(x,y),
\qquad
T'(x,y,z) = \delta T(z)h(x,y).
\end{equation}
We here assume that $\overline{h} = 0$ and $\overline{h^2} \neq 0$.
We can then express the convective flux in terms of these vertically-varying profiles and an average over the horizontal structure of the flows,
\begin{equation}
\Fconv \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
\label{eqn:Fconv_vertical}
\end{equation}
In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must be oppositely signed and the convective flows should eventually come to a stop through buoyancy breaking.
This is achieved through a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
\begin{equation}
\frac{1}{2}\frac{d w^2}{dz} = |\alpha| g T'.
\end{equation}
Multiplying both sides by $h(x,y)$, taking a horizontal average, and then substituting $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation,
\begin{equation}
\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 = \Fconv dz.
\label{eqn:theory_ode}
\end{equation}
This equation can be integrated over the depth of the convection zone from $W = 0$ to $W = W_0$ at the convective boundary, as well as over the penetration zone from $W = W_0$ to where $W = 0$.
We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
Integrating Eqn.~\ref{eqn:theory_ode} over the CZ and PZ and taking a ratio of these two equations, we find
\begin{equation}
-\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} = 
\frac{\int_{\rm{PZ}} \Fconv dz}{\int_{\rm{CZ}} \Fconv dz}.
\label{eqn:theory_fraction}
\end{equation}
In order to move further with this theory, it is necessary to specify the vertical shape of $\Fconv$, which is in turn set by $Q$, $\gradad$, and $k$.
We will assume that $\gradad$ has a constant value and that the internal heating $Q$ is localized near the bottom of the CZ so that a constant convective flux $\Fcz$ is carried in the bulk convection zone.
As a result, the vertical profile of $\Frad$ and $\Fconv$ is determined completely by the behavior of $k(z)$ near the convective boundary.
We will study two cases in this work: a discontinuous jump in $k(z)$ at the convective boundary, and a piecewise-linear profile of $k(z)$ whose derivative may be discontinuous at the convective boundary.

\subsection{Case I: Discontinuous radiative conductivity}
We first consider a radiative conductivity $k(z)$ which is discontinuous, with a value of $k_{\rm{CZ}}$ in the convection zone and larger value $k_{\rm{RZ}}$ in the PZ and radiative zone (RZ).
The values of $k$ are chosen so that the convective flux follows
\begin{equation}
\Fconv(z) = \begin{cases}
\Fcz			&	z \leq \Lcz,\\
-\mP_D^{-1} \Fcz & 	z > \Lcz 
\end{cases}.
\end{equation}
Here, $\mP_D^{-1}$ is the ``penetration parameter'' (subscript D for discontinuous case).
Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = \Lcz$ and the penetration zone from $z = \Lcz$ to $z = \Lcz + \dP$,
\begin{equation}
\frac{\dP}{\Lcz} = \mP_D
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}.
\label{eqn:discontinuous_prediction}
\end{equation}
We then see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the horizontal structure of the convective dynamics in the PZ and the CZ.
This makes sense; As $\mP_D$ grows, the magnitude of $\Fconv$ in the PZ shrinks, and so too does the breaking force of buoyancy.

\subsection{Case II: Piecewise linear radiative conductivity}
We next assume that $k(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be.
As a result, the convective flux in the vicinity of the boundary takes the form
\begin{equation}
\Fconv(z) = 
\begin{cases}
(\partial_z k)_{\rm{cz}}\gradad (\Lcz - z) & z \leq \Lcz \\
-\mP_L^{-1}(\partial_z k)_{\rm{cz}}\gradad (z - \Lcz) & z > \Lcz
\end{cases},
\end{equation}
where we assume that $(\partial_z \Frad)_{\rm{cz}} =  (\partial_z k)_{\rm{cz}}\gradad$ is a constant.
Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
\begin{equation}
\frac{\dP}{\Lcz} = \sqrt{\mP_L
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}},
\label{eqn:linear_prediction}
\end{equation}
which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.

\section{Simulation Details}
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q
\end{align}
